Analysis of the \\ Information Security Job Landscape \\ in Austria

### 2020-05-27 paper/paper.tex
Fix line break.

After choosing \textit{ScrapeStorm}, we started by setting up the crawlers. The websites we wanted to scrape are \texttt{monster.at} \cite{monster}, \texttt{at.indeed.com} \cite{indeed} and \texttt{stepstone.at} \cite{stepstone}.

>>>>

After choosing \textit{ScrapeStorm}, we started by setting up the crawlers. The websites we wanted to scrape are \texttt{monster.at}~\cite{monster}, \texttt{at.indeed.com}~\cite{indeed} and \\ \texttt{stepstone.at}~\cite{stepstone}.
